---
title: "fitzRoy v1.7.0 on CRAN"
author: "James Day"
date: "2025-03-12"
execute:
  error: TRUE
---

I'm pleased to announce that fitzRoy v1.7.0 has just been accepted to CRAN!

You can read about all the changes below.

```{r prep, eval=TRUE, include=TRUE}
library(fitzRoy)
```

## New Features

### Fantasy and Supercoach scores

New functions have been added to fetch AFL Fantasy (Dream Team) and Supercoach round scores from Footywire.

-   `fetch_scores()` - Wrapper function to fetch either scoring system. Specify `type = "supercoach"` or `type = "dream_team"` along with a year and rounds.
-   `fetch_supercoach_scores()` - Fetch Supercoach scores directly.
-   `fetch_fantasy_scores()` - Fetch AFL Fantasy scores directly.

```{r fetch_scores, eval=TRUE, include=TRUE}
fitzRoy::fetch_scores(type = "supercoach", year = 2025, rounds = 1) |> head()
fitzRoy::fetch_scores(type = "dream_team", year = 2025, rounds = 1) |> head()
```

Each returns player-level data for the specified rounds, including rank, salary, round score, and value.

### AFL Awards

A new `fetch_awards()` wrapper function has been added to retrieve data for three major AFL awards from Footywire.

-   `fetch_awards_brownlow()` - Returns player and team Brownlow vote tallies for a given season.
-   `fetch_awards_allaustralian()` - Returns the final All-Australian team (22 players) or the initial squad (44 players).
-   `fetch_rising_star()` - Returns Rising Star nominations and round-level performance stats.

```{r fetch_awards_brownlow, eval=TRUE, include=TRUE}
# Player vote tallies
fitzRoy::fetch_awards(2024, award = "brownlow", type = "player")

# Team vote summary
fitzRoy::fetch_awards(2024, award = "brownlow", type = "team")
```

```{r fetch_awards_allaustralian, eval=TRUE, include=TRUE}
fitzRoy::fetch_awards(2023, award = "allaustralian", type = "team")
fitzRoy::fetch_awards(2023, award = "allaustralian", type = "squad")
```

```{r fetch_awards_risingstar, eval=TRUE, include=TRUE}
# All nominations for the season
fitzRoy::fetch_awards(2024, award = "risingstar", type = "nominations")

# Stats for a specific round's nominees
fitzRoy::fetch_awards(2024, award = "risingstar", round_number = 5, type = "stats")
```

### Out-of-contract players

`fetch_outofcontract()` returns a list of players whose contracts expire at the end of a given year — useful for team list analysis and end-of-season trade period research. Data is available from 2025 onwards.

```{r fetch_outofcontract, eval=TRUE, include=TRUE}
fitzRoy::fetch_outofcontract(year = 2026)
```

### Team statistics

A new `fetch_team_stats()` wrapper has been added for retrieving team-level aggregate statistics. It supports three sources: AFL Tables, Footywire, and VFL Stats.

```{r fetch_team_stats, eval=TRUE, include=TRUE}
# Team totals from AFL Tables
fitzRoy::fetch_team_stats(2024, summary_type = "totals", source = "afltables")

# Per-game averages from Footywire
fitzRoy::fetch_team_stats(2024, summary_type = "averages", source = "footywire")

# VFL Men's team stats
fitzRoy::fetch_team_stats(2024, source = "vflstats", comp = "VFLM")
```

## Bug Fixes

-   Fixed duplicates for most recent game in `fetch_player_stats_afltables()` ([#250](https://github.com/jimmyday12/fitzRoy/issues/250))
-   Fixed issues for `fetch_player_details` when indigenous names are used ([#261](https://github.com/jimmyday12/fitzRoy/issues/261), [#262](https://github.com/jimmyday12/fitzRoy/issues/262))
-   Updated `replace_teams()` to handle the new AFL.com.au spelling of *Wallitj Marawar* ([#259](https://github.com/jimmyday12/fitzRoy/issues/259))
-   Fixed issue with `fetch_player_footywire_stats` not working with the new season

Enjoy!
