---
title: "fitzRoy v1.3.0 on CRAN"
author: "James Day"
date: "2023-03-02"
---

I'm pleased to announce that `fitzRoy` v1.3.0 has just been accepted to CRAN!

This update mostly contains bug fixes. You can read about them below.

### Deprecated functions

All of the `get_` family of functions are now formally following the deprecation lifecycle used in the [{lifecycle} package](https://lifecycle.r-lib.org/articles/stages.html). That is, there is now a formal warning for using these functions. The next version of `fitzRoy` will hard deprecate these functions, where calling them will return an error. Given these have been technically deprecated since v1.0.0, this is plenty of warning.

```{r}
# install.packages("fitzRoy")
library(fitzRoy)

fitzRoy:::get_fixture(2020)
```

### `fetch_player_stats_afl`

Fixed an issue with `fetch_player_stats_afl` where an error was being returned for the new season. It now returns NULL if there is no data for the specified season

```{r}
fetch_player_stats_afl(2023, round_number = 1)

```

### Debut players in `fetch_player_stats_afltables`

Fixed an annoying bug where players who debuted in 2023 were getting assigned an ID of 0 in AFL Tables Data. This is now resolved and all ID's should be correctly assigned for new players

```{r}
df <- fetch_player_stats_afltables(2022)

df |> 
  dplyr::filter(ID == 0)
```

### Smaller Bug Fixes

-   Fixed a range of unhelpful messages and warnings

-   Fixed a bug in `fetch_player_stats_footywire` that was caused by an update to the website

Enjoy!
